---
title: "CoreLogic"
author: "Chris Eshleman"
date: "TBD"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(olsrr) 
```


- Check for outliers or influential observations. 
- Check index and other covariates for necessary transformations. Visual for the predictors and also a whatchamacallit for the index itself. 
- Subset selection of inputs on index. Correlation analysis from there. Then machine learning on leftovers, consider adding to the mix. Does the best-scoring input really deviate strongly from the index? 
- Treat the index as continuous. Technically, an index from 1-100 isn’t a pure continuous (quantitative) variable but it falls closer to that than other variable types. 
- Potential follow-up: check variation of crime statistics across the Conrex-non Conrex divide. (Just use MSA designations.) 

### Index 
```{r}
summary(mtcars) 
plot(mtcars$disp[order(mtcars$disp)]) 
```

```{r}
fit = lm(disp ~ ., data = mtcars) 
summary(fit)
plot(fit)

library(MASS)
boxcox(fit,lambda=seq(-2,2,0.5)) 
boxcox(fit,lambda=seq(-1,1,0.5)) 

fit2 = lm(1/sqrt(disp) ~ ., data = mtcars) 
plot(fit2)
```

### Outliers 

```{r}
ols_plot_cooksd_bar(fit) 
ols_plot_resid_lev(fit)
ols_plot_resid_stud_fit(fit)
#plot(Q2.Dev$Sales.price,exp(m.q2.f$fitted.values), col='blue', pch=16, ylab= "Predicted Sales.price", xlab= "Actual Y",main="Regression Model")
```


### Initial selection 

```{r}
fit.selex = ols_step_best_subset(fit) 
fit.selex 
plot(fit.selex) 
#plot(1:8,fit.selex$aic,xlab="Number of Predictors",ylab="AIC")
```




```{r}
#selex = data.frame(disp ~ cyl + hp + wt + qsec + carb) 
```


```{r}
fit2 = lm(disp ~ cyl + hp + wt + qsec + carb, data = mtcars) 
```

